% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}                     % Add 'print' as an option into the [] to remove colors for printing.
\sethyphenation[variant=british]{english}{}    % Add words between the {} to avoid them to be cut 

\begin{document}

\header{Milad}{Irannejad}                      % First name and last name
\lastupdated


%----------------------------------------------------------------------------------------------------
%  SIDEBAR SECTION  --  In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------------------

\begin{aside}
%
\section{Contact}
% 1000 Wildwood Dr
% Newmarket, ON  L3Y 2B5
Toronto, ON  CANADA
~
+1 (416) 880 6955
\href{mailto:moorara@gmail.com}{moorara@gmail.com}
~
\href{https://milad.dev}{milad.dev}
\href{https://github.com/moorara}{github.com/moorara}
\href{https://linkedin.com/in/moorara}{linkedin/in/moorara}
\href{https://medium.com/@moorara}{medium/@moorara}
%
\section{Computer Science}
Algorithms
Data Structures
Distributed Systems
% Machine Learning
%
\section{Programming}
Go, Python, Ruby
JavaScript, TypeScript
% Java, C\#, C/C++
%
\section{Development}
OOP, TDD
Design Patterns
Domain-Driven Design
%
% \section{Frontend}
% React, Redux
% Progressive Web Apps
%
\section{Cloud Computing}
Cloudflare
Google Cloud Platform
Amazon Web Services
% Microsoft Azure
%
\section{DevOps/SRE}
Infra-as-Code
Immutable Infra
% Packer
Terraform, Vault
Kubernetes, Containers
Automation, CI/CD
GitOps, Helm
Autoscaling
% Service Mesh
Observability
Monitoring
Elasticsearch, Kibana
Prometheus, Grafana
OpenTelemetry, Jaeger
Teleport, PagerDuty
% Datadog
%
\section{Database}
Postgres, BigQuery
MongoDB, Redis
%
\section{Backend}
Microservices
Serverless
REST, gRPC, GraphQL
OAuth 2.0, OIDC
% Kafka, NATS
% RabbitMQ
%
% \section{Newbie}
% Machine Learning
% TensorFlow
% Blockchain
%
\end{aside}


%----------------------------------------------------------------------------------------------------
%  OBJECTIVE/HIGHLIGHTS SECTION
%----------------------------------------------------------------------------------------------------

\section{Highlights}

%I enjoy building meaningful and impactful things.
%I am passionate about building highly available, scalable, reliable, and autonomous systems.
%I am also interested in improving the developer experience and software delivery performance.
%(more about me \href{https://milad.dev/about}{here})

\begin{itemize}
  \setlength{\itemsep}{-4pt}
  \item \textbf{10+ years} in Cloud Computing, Microservices, and Automation
  \item \textbf{8+ years} with Go programming
  \item \textbf{6+ years} in IaC, DevOps, SRE, Observability, and Monitoring
\end{itemize}


%----------------------------------------------------------------------------------------------------
%  WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}

  \entry
  {\small Dec22--Now}
  {Senior Site Reliability Engineer - GitLab}
  {Remote, Canada}
  {
    \begin{itemize}
      \item Managed Kubernetes clusters, upgrades, and monitoring.
      \item Migrated Cloudflare Pages Rules to Rulesets, optimizing cache.
      \item Upgraded HAProxy with zero downtime; resolved a critical \href{https://github.com/haproxy/haproxy/issues/2262}{bug} in HAProxy.
      \item Implemented GitOps with Flux and ArgoCD, leading the initial evaluation.
      \item Enabled IPv6 and migrated load balancers with zero downtime.
      \item Implemented the Teleport platform, automated processes, and integrated with SIEM.
      \item Led technical and behavioral interviews for hiring initiatives.
      \item Handled on-call incidents, reviews, and improvements.
      \item Improved internal runbooks and public documentation.
      \item Collaborated with teams and supported customers on urgent tasks.
    \end{itemize}
    \textbf{Technologies:} Cloudflare, GKE, EKS, Helm, Postgres, Go, Terraform, Vault, Prometheus, Grafana, etc.
  }

  \entry
  {\small Sep21--Jul22}
  {Senior Production Engineer - Shopify}
  {Remote, Canada}
  {
    \begin{itemize}
      \item Managed, upgraded, and monitored GKE clusters for core infrastructure.
      % \item Facilitated the migration from Docker to containerd across infrastructure teams.
      % \item Contributed to large-scale test preparations and execution.
      \item Bootstrapped new regions, expanding global infrastructure.
      \item Improved Shopify’s custom Kubernetes controller for optimized scaling.
      \item Performed capacity planning and provisioning for core infrastructure.
      \item Participated in on-call rotations, responding to incidents and supporting other teams.
    \end{itemize}
    \textbf{Technologies:} Cloudflare, GKE, Kubernetes, Postgres, Go, Terraform, etc.
  }

  \entry
  {\small Jan20--Aug21}
  {Software Engineer II - Uber}
  {Remote, Canada}
  {
    \begin{itemize}
      \item Contributed to the development and launch of Uber Eats Ads.
      \item Implemented Ads Platform campaign management service.
      \item Developed the GraphQL backend for Ad Platform APIs.
      \item Participated in on-call shifts, managing Ads platform production incidents.
      \item Authored and reviewed engineering design documents.
      % \item Collaborated closely with remote teams, product managers, and data scientists.
    \end{itemize}
    \textbf{Technologies:} Go, Bazel, Kafka, Docstore, HIVE, JavaScript, React, GraphQL, etc.
  }

  \entry
  {\small Oct18--Dec19}
  {Senior Backend Engineer - Flybits}
  {Toronto, ON, Canada}
  {
    \begin{itemize}
      \item Led microservices development and created core Go libs for observability.
      % \item Developed and implemented a testing strategy for engineering teams.
      \item Implemented observability using structured logging, metrics, and tracing.
      \item Created modular CI/CD pipelines and an efficient release process.
      \item Automated Kubernetes CI/CD workflows using GitOps and Flux.
      %\item Managed a platform team of engineers and co-op students.
      %\item Conducted interviews and onboarded new team members.
    \end{itemize}
    \textbf{Technologies:} AWS, Microservices, Kubernetes, Docker, Go, MongoDB, PostgreSQL, RabbitMQ, etc.
  }

  \entry
  {\small Feb16--Sep18}
  {Software Engineer - Qlik}
  {Ottawa, ON, Canada}
  {
    % \begin{itemize}
    %  \item Helped with developing a reliable and scalable cloud platform.
    %  \item Contributed to delivering Qlik Sense Cloud for Business (QSCB).
    %  \item Contributed to building the hybrid cloud platform for Qlik's Multi-Cloud Solution.
    % \end{itemize}
    \textbf{Technologies:} AWS, Microservices, Terraform, Kubernetes, Docker, Go, Node.js, MongoDB, NATS, Helm.
   }

  \entry
  {\small Jan15--Apr15}
  {Software Tools Development Student - BlackBerry}
  {Waterloo, ON, Canada}

  % \entry
  % {\small Nov11--Sep12}
  % {Software Developer - Farazpardazan}
  % {Tehran, Iran}

  % \entry
  % {\small 2009--2010}
  % {Software Engineer - IRAMOT}
  % {Tehran, Iran}
  % {}

\end{entrylist}


%----------------------------------------------------------------------------------------------------
%  EDUCATION SECTION
%----------------------------------------------------------------------------------------------------

\newpage
\section{Education}

\begin{entrylist}

  \entry
  {\small 2013--2015}
  {M.Sc. in Software Engineering {\normalfont [GPA: 87.80/100]}}
  {University of Waterloo}
  {Thesis: Identifying Defects Related to the Order in which Messages are Received in Message-Passing Systems \\
   Course Summary: Methods and Tools for Software Engineering, Distributed Systems, Computer-Aided Verification, Statistics in Engineering \\
   Scholarships: Faculty of Engineering Graduate Scholarship (x2), Graduate Research Studentship (x7), and International Master's Student Award (x6)}

  \entry
  {\small 2006--2011}
  {B.Sc. in Software Engineering {\normalfont [GPA: 16.69/20]}}
  {Amirkabir University of Technology}
  {Thesis: Finding Expert Users in Java Forums using Social Network Analysis \\
   Course Summary: Algorithms Design, Data Structures, Database Design, Artificial Intelligence, Information and Communication Security, Data Mining, Compilers Design, Software Engineering, Internet Engineering, Information Retrieval}

\end{entrylist}


%----------------------------------------------------------------------------------------------------
%  PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------------------

\section{Publications}

\begin{entrylist}

  \entry
  {\small July 2017}
  {\href{http://ieeexplore.ieee.org/abstract/document/7964877}{A Reordering Framework for Testing Message-Passing Systems}}
  {Toronto, ON, Canada}
  {\small{2017 IEEE 20th International Symposium on Real-Time Distributed Computing (ISORC)}}

\end{entrylist}


%----------------------------------------------------------------------------------------------------
%  PROJECTS SECTION
%----------------------------------------------------------------------------------------------------

\section{Projects}

Please visit my \href{http://github.com/moorara}{GitHub} page for the full list of open-source contributions, side projects, etc.

\textbf{github.com/moorara/algo} Advanced algorithms and data structures for Go \\
\textbf{github.com/gardenbed/basil} an application framework and CLI tool for Go  \\
\textbf{github.com/gardenbed/changelog} generate elegant change logs for GitHub repositories  \\
\textbf{github.com/moorara/gocert} generating self-signed SSL/TLS certificate chain made easy \\

\begin{entrylist}

  %\entry
  %{\small Jun11--Oct11}
  %{Finding Expert Users in Java Forums}
  %{Amirkabir University of Technology}
  %{I applied an improved version of the PageRank algorithm to a weighted graph of users based on the relevance of
  % their posts to a specific topic in Java Technology Concept Map to rank the knowledge of users on a specific topic in Java.}

  % \entry
  % {\small Sum. 2009}
  % {Vector Model Search Engine}
  % {Amirkabir University of Technology}
  % {I designed and implemented a search engine for many unstructured documents in Java.
  % I practiced handling data that cannot be fit in memory, parsing data streams, indexing, clustering, and searching.}

\end{entrylist}


%----------------------------------------------------------------------------------------------------
%  SKILLS SECTION
%----------------------------------------------------------------------------------------------------

% \section{Skills}

% \textbf{Computer Science:} Algorithms, Data Structures, Distributed Systems, Machine Learning \\
% \textbf{Programming Languages:} Go, Rust, JavaScript, TypeScript, Python, Ruby, Java, C\#, C/C++ \\
% \textbf{Database:} MongoDB, ArangoDB, CockroachDB, PostgreSQL \\
% \textbf{Backend:} Microservices, Serverless, REST, gRPC, GraphQL, NATS, Kafka \\
% \textbf{Containerization:} Docker, Kubernetes, Service Mesh, Kustomize, Helm \\
% \textbf{Frontend:} Progressive Web Applications, React, Redux, Relay, Vue \\
% \textbf{Testing:} Unit Testing, Component Testing, Integration Testing, System Testing \\
% \textbf{DevOps/SRE:} Automation, Continuous Integration, Continuous Delivery, GitOps \\
% \textbf{Monitoring:} OpenTelemetry, Elasticsearch, Kibana, Prometheus, Grafana, OpenTracing, Jaeger \\
% \textbf{Infrastructure:} Infrastructure-as-Code, Immutable Infrastructure, Packer, Terraform, Vault \\
% \textbf{Cloud Computing:} Amazon Web Services, Google Cloud Platform, Microsoft Azure \\
% \textbf{Programming Paradigms:} Object-Oriented, Event-Driven, Functional \\
% \textbf{Development Methods:} TDD/BDD, Design Patterns, Domain-Driven Design \\
% \textbf{Agile:} Scrum, Kanban, Scrumban \\


%----------------------------------------------------------------------------------------------------
%  CERTIFICATION SECTION
%----------------------------------------------------------------------------------------------------

% \section{Certifications}

% \begin{entrylist}

  % \entry
  % {\small Feb 2016}
  % {Big Data Specialization}
  % {Coursera Verified Certificates}
  % {Courses:
  % \begin{itemize}
  %   \item \href{http://coursera.org/verify/WUHGJVM43XRY}{Introduction to Big Data}
  %   \item \href{http://coursera.org/verify/Q7FQMKACTV5G}{Hadoop Platform and Application Framework}
  %   \item \href{http://coursera.org/verify/BQ4G2ZLX8KP7}{Introduction to Big Data Analytics}
  %   \item \href{http://coursera.org/verify/Y8WH9EQ2YVMM}{Machine Learning with Big Data}
  % \end{itemize}}

  % \entry
  % {\small Jul 2015}
  % {MongoDB for Node.js Developers}
  % {MongoDB, Inc.}
  % {Verify at \href{http://education.mongodb.com/downloads/certificates/6c901548426b4c91b2fc8d594c14ce27/Certificate.pdf}{education.mongodb.com}}

  % \entry
  % {\small Nov 2014}
  % {Web Application Architectures}
  % {Coursera Verified Certificates}
  % {Verify at \href{http://coursera.org/verify/GGEQVNQNY7}{coursera.org/verify/GGEQVNQNY7}}

  % \entry
  % {\small Sept 2014} 
  % {Software Security}
  % {Courser Verified Certificates}
  % {Verify at \href{http://coursera.org/verify/5RLL8447KM}{coursera.org/verify/5RLL8447KM}}

% \end{entrylist}


%----------------------------------------------------------------------------------------------------
%  REFERENCES SECTION
%----------------------------------------------------------------------------------------------------

\section{References}

References will be provided upon request.
Please visit my \href{http://linkedin.com/in/moorara}{LinkedIn} page for references, accomplishments, etc.

% \textbf{Jim Reed:} Senior Manager at Qlik, (jim.a.reed@gmail.com) \\
% \textbf{Christophe Cornu:} Senior Architect at Qlik, (christophe.cornu@gmail.com) \\
% \textbf{Sebastian Fischmeister:} Associate Professor at University of Waterloo (sfischme@uwaterloo.ca) \\


%----------------------------------------------------------------------------------------------------
%  POSTSCRIPT
%----------------------------------------------------------------------------------------------------


% text ...


%----------------------------------------------------------------------------------------------------
%  END
%----------------------------------------------------------------------------------------------------


\end{document}
